Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-29 manuscript.Rmd
Update CRQA results

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference from chance for maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for maxL and LAM. All other metrics
were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and LAM (Figure
\@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistical difference from chance for rENTR. All other
metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

>>>>

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference from chance for DET, NRLINE, and maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, maxL, and LAM. All other metrics
were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM (Figure
\@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found no statistical difference from chance for and metrics (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).
